External priors for the next generation of CMB experiments.

### 2016-02-09 Notes/response.txt

- In the introduction: Ref. 4 is WMAP 1year results, in this context
the general WMAP experiment paper Bennett et al. 2003 or the final
mission results Bennet et al. 2012 would be more appropriate. Same
thing for Planck, cite the Blue Book and/or the 2015 Overview papers.
Ref. 5 is Maxima and Ref. 6 is Boomerang, they are not satellites and
are not mentioned in the text.

Thanks, Fixed adding Bennett et al. 2003 and Blue book

- ACT and SPT did not follow DASI, they have measured temperature with
ACTPol and SPTPol going for polarization. The first two should go into
the above temperature discussion with references to latest results or
general papers describing the experiments, and the last two should
contribute to the polarization discussion.

We organized the discussion into ground base and satellite experiments. For this reason
we mentioned ACT and SPT toghether with DASI. We added references to general papers
describing actpol and sptpol.

@@

- In the introduction the cosmological dependence on neutrinos
properties jumps from number to masses to number again, it is
confusing please rephrase.

We introduce the two main topics of that paragraph (N_eff and M_nu) in the first sentence and we then
describe one after the other in the remaining. We strengthen the connector, hopefully reducing the confusion.

@@

- Choose between Universe or universe.

Done

- Define the cosmological parameters listed in the introduction.

The parameters used in our pipelines are quite standard in the field, and we think that pointing the
reader to the Planck cosmology paper is probably enough.

@@

- Section IIIA, add a reference to oscillation experiments result.

Done.

- Section IIIA, measuring ell<50 is not a design goal but rather an
analysis one given that the problem is the atmospheric emission.

We rephrase it --> If CMB S4 will not be designed to measure scales l < 50 to avoid difficulties in dealing with atmospheric emission

### 2016-02-09 Notes/CMBS4_priors_paper.tex
typos fixed

Much of the improvement that would come on neutrino masses and $w$ from $H_0$ or $\Omega_ch^2$ priors is anticipated to be provided by distance measurements made by DESI. But, additional $H_0$ measurements beyond DESI would help, as evidenced by the sharply falling curves in the left-most regions of \reffig{prior_omeganuh2} and \reffig{ellipse_w_H0}. Indeed, perhaps the most tantalizing finding is that future surveys beyond DESI and LSST \cite{lsst-dark-energy-science-collaboration:2012} that would tighten the constraints on, say, the baryon density and $n_s$ could indirectly lead to constraints in $N_{\rm eff}$ much less than a percent. Given the power of these constraints to probe physics beyond the Standard Model, such surveys seem particularly interesting to pursue.

>>>>

Much of the improvement that would come on neutrino masses and $w$ from $H_0$ or $\Omega_ch^2$ priors is anticipated to be provided by distance measurements made by DESI. But, additional $H_0$ measurements beyond DESI would help, as evidenced by the sharply falling curves in the left-most regions of \reffig{prior_omeganuh2-h}, \reffig{prior_omeganuh2-50-h} and \reffig{ellipse_w_H0}. Indeed, perhaps the most tantalizing finding is that future surveys beyond DESI and LSST \cite{lsst-dark-energy-science-collaboration:2012} that would tighten the constraints on, say, the baryon density and $n_s$ could indirectly lead to constraints in $N_{\rm eff}$ much less than a percent. Given the power of these constraints to probe physics beyond the Standard Model, such surveys seem particularly interesting to pursue.
